---
title: "PESI stimulus selection"
author: "Irene S. Plank"
date: "15/02/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rMEA)
library(devtools)
library(stringr)
library(BayesFactor)
source("createDFsync.R")

knitr::opts_knit$set(root.dir = "/home/iplank/Insync/10planki@gmail.com/Google Drive/NEVIA/study_IMPAS/MEA_sync")

```

<style type="text/css">
.main-container {
  max-width: 1100px;
  margin-left: auto;
  margin-right: auto;
}
</style>

# Introduction

Script to read in MEA data, preprocess it and compute CCF based synchrony for each dyad. The script needs the MEA files separated by location (Munich or Cologne), group (ASD or TD) and fps in separate folders. The folder names are:

* "./MEA txt files_5min_t15_Cologne/TD-ASD/24fps"
* "./MEA txt files_5min_t15_Cologne/TD-ASD/24fps"
* "./MEA txt files_5min_t15_Cologne/TD-ASD/25fps"
* "./MEA txt files_5min_t15_Cologne/TD-ASD/25fps"

The script produces a csv file with the selected videos.

# Motion Energy Analysis

```{r mea}
# initialisation of all settings
st  = 1          # start times (seconds)
sz  = 10         # window size for ccf (seconds)
inc = sz
lg  = 3          # lag for ccf (seconds)

# 25fps -------------------------------------------------------------------

fps = 25

## COLOGNE SAMPLE

# read in total ROI data of ASD dyads
mea_ASD_head_C = readMEA("./MEA txt files_5min_t15_Cologne/TD-ASD/25fps",
                           sampRate=fps, 
                           skip=st*fps,
                           s1Col = c(1), s2Col = c(3), 
                           s1Name = "L_head", s2Name = "R_head", 
                           header = F,
                           idOrder = c("id","group"),
                           idSep = "_",
                           sep = "")

mea_ASD_head_C = setGroup(mea_ASD_head_C, "ASD")

## read in total ROI data of TD dyads
mea_TD_head_C = readMEA("./MEA txt files_5min_t15_Cologne/TD-TD/25fps",
                          sampRate=fps, 
                          skip=st*fps,
                          s1Col = c(1), s2Col = c(3), 
                          s1Name = "L_head", s2Name = "R_head", 
                          header = F,
                          idOrder = c("id","group"),
                          idSep = "_",
                          sep = "")

mea_TD_head_C = setGroup(mea_TD_head_C, "TD")

## Combine into a single object
mea_all_head = c(mea_ASD_head_C, mea_TD_head_C)

## Preprocessing and calculations
mea_all_head = MEAscale(mea_all_head)

## Run CCF analysis 
mea_all_head = MEAccf(mea_all_head, lagSec=lg, winSec=sz, incSec=inc, r2Z=T, ABS=T)

## put information into the dataframe 
df.head = createDFsync(mea_all_head, sep = "_", desc = c("group", "dyad", "session"), fps)

df.head = df.head %>%
  rename("context" = "group") %>%
  mutate(
    context = as.factor(context), 
    context = recode_factor(context, 
      'ASD' = "heterogeneous",
      'TD'  = "homogeneous"
    )
  ) %>% select(-session)

# create total motion variables for each dyad
df.head$mot = rowMeans(df.head[,c("s1mot","s2mot")])
df = df.head

# filter out windows with extreme motion 
df.head = df %>% ungroup() %>%
  mutate(
    upper = quantile(mot, probs=c(0.75), na.rm = T), 
    lower = quantile(mot, probs=c(0.25), na.rm = T)
  ) %>%
  filter(lower <= mot & mot <= upper) %>%
  drop_na() %>% filter(
    dyad != "D28g"
  )
```

# Choose videos

```{r vid_sel}
df.head_agg = df.head %>% group_by(context, dyad) %>%
  summarise(
    n_win = n()
  )

# select the n videos of each dyad with the highest and the n with the lowest synchrony values (peak)
n = 4 # number of windows per condition per video
vid_sel_high = df.head %>%
  arrange(desc(peak)) %>% 
  group_by(dyad) %>%
  slice(1:n) %>%
  mutate(
    sync = "high"
  )

vid_sel_low = df.head %>%
  arrange(peak) %>% 
  group_by(dyad) %>%
  slice(1:n) %>%
  mutate(
    sync = "low"
  )

# add frame for start and end

vid_sel = rbind(vid_sel_low, vid_sel_high) %>%
  mutate(
    frame_sta = as.numeric(substr(winst,5,5))*60*fps + as.numeric(substr(winst,7,8))*fps,
    frame_end = as.numeric(substr(winen,5,5))*60*fps + as.numeric(substr(winen,7,8))*fps
  )

```

# Check peaks and motion

```{r peaks}

# are the high sync videos higher in synchrony than the low sync?
boxplot(vid_sel[vid_sel$sync == "high",]$peak, vid_sel[vid_sel$sync == "low",]$peak)

# are there context specific differences in synchrony and motion - which we want to avoid!
boxplot(vid_sel_high[vid_sel_high$context == "heterogeneous",]$peak, vid_sel_high[vid_sel_high$context == "homogeneous",]$peak)
boxplot(vid_sel_low[vid_sel_low$context == "heterogeneous",]$peak, vid_sel_low[vid_sel_low$context == "homogeneous",]$peak)

shapiro.test(vid_sel_high[(vid_sel_high$context == "homogeneous"),]$peak)
shapiro.test(vid_sel_high[vid_sel_high$context == "heterogeneous",]$peak)
shapiro.test(vid_sel_low[(vid_sel_low$context == "homogeneous"),]$peak)
shapiro.test(vid_sel_low[vid_sel_low$context == "heterogeneous",]$peak)

ttestBF(vid_sel_high[vid_sel_high$context == "heterogeneous",]$peak, vid_sel_high[vid_sel_high$context == "homogeneous",]$peak, paired = F)
ttestBF(vid_sel_low[vid_sel_low$context == "heterogeneous",]$peak, vid_sel_low[vid_sel_low$context == "homogeneous",]$peak, paired = F)

# Check motion ------------------------------------------------------------
boxplot(vid_sel_high[vid_sel_high$context == "heterogeneous",]$mot, vid_sel_high[vid_sel_high$context == "homogeneous",]$mot)
ttestBF(vid_sel_high[vid_sel_high$context == "heterogeneous",]$mot, vid_sel_high[vid_sel_high$context == "homogeneous",]$mot, paired = F)

write_csv(vid_sel, file="PESI_videosel-full_230404.csv")

```